method

### 2021-12-02 06_Paper/ER-ED/method.Rmd

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
```

@@

  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["instr_1"]],datalist_ER[[i]][["slider_arousal.response"]],datalist_ER[[i]][["slider_effort.response"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)),]

@@

for (i in 1:length(datalist_ER)) {
  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["resp_choice.keys"]])
  colnames(tmp) = names(data_choice)
  tmp = tmp[(!is.na(tmp$choice)),]

>>>>

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
```

@@

  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["instr_1"]], datalist_ER[[i]][["slider_arousal.response"]], datalist_ER[[i]][["slider_effort.response"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)), ]

@@

for (i in 1:length(datalist_ER)) {
  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["resp_choice.keys"]])
  colnames(tmp) = names(data_choice)
  tmp = tmp[(!is.na(tmp$choice)), ]
